Followers Are Not Enough: A Multi-faceted Approach to Community Detection in Online Social Networks

### 2014-11-24 paper-postreview/results.tex

%\subsection{Qualitative Analysis of Community Memberships Across Types}
\subsection{Answering the Questions}

@@

In the previous sections we showed how the communities emerging from the different weightings of the follower-followee network differ quantitatively both at the macro and at the micro scale. Here we present some concrete examples of such different communities, in order to show more precisely the interest of using a multifaceted approach to community detection. We explore this at two scale: firstly at the community level, and then at the individual level.

@@

As a sanity check, it is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types had the highest PV-AC. Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee. Said differently, users with the highest PV-AC in an activity-based community provide the highest reduction in uncertainty about that communities activity or inactivity on Twitter. Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency. This means that these accounts had high predictive capacity in terms of their followers' activity on Twitter. This is not surprising as these activity-based communities heavily overlapped with the topic-based communities that discuss Colorado (mentioned above) and these accounts provide information on this topic. This provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity for a communities activity on a social media network. However, more work needs to be done to quantify this more fully.

Lastly, it is interesting to note that two of the Forbes ``Top 10 Social Media Influencers", happen to be in our network, \emph{viz.}, Ann Tran and Jessica Northey, and transfer entropy also quantified these two users as having high PV-AC, i.e., the uncertainty about their followers activity on Twitter was reduced given their tweet histories. While we do not believe this information theoretic measure can capture social influence in its entirety, 
% members, as categorized by transfer entropy. 
this suggests that this activity-based measure may be useful in finding influential members purely based on their temporal tweet history; even completely ignoring both tweet content and social status. However, a deeper analysis would need to be carried out to verify this finding.

On an individual-based level, we also found some interesting cases of membership to different communities, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to. 
For example, the user @JohnReaves belongs to two different topic communities: one talking about healthcare and the other talking about innovation and creativity. There is a almost $70\%$ overlap between the users in the innovation and creativity topic community and the interaction-based community and the activity-based community the user is in, whereas there is almost no overlap between these two and the healthcare community. This means that he interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
Secondly, user @jenajean also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave alike people in that communities, whereas she also talks a lot about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado (and to only that topic community). The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they belong to different interaction-based communities, each of which does not overlap with the topic community a part for one or two users. Therefore they interact with other groups of people.

>>>>

%\subsection{Qualitative Analysis of Community Memberships Across Types}
%\subsection{Answering the Questions}
\subsection{Uncovering the Multifacetedness of Community Memberships}

@@

In the previous sections we showed that the communities emerging from the different weightings of the structural network quantitatively differ both at the macroscopic and at the microscopic scale. Here, we present some concrete examples of different community membership, in order to uncover the interest of using a multifaceted approach to community detection. We explore this at two scales: firstly at the community level, and then at the individual level.

@@

As a sanity check, it is interesting to examine the intersection between this topic-based community and the overlapping activity-based communities and explore which users in the intersection of these community types have the highest PV-AC. Recall that this refers to a reduction in uncertainty about a follower(s) activity on Twitter given the tweet history of a followee. Said differently, users with the highest PV-AC in an activity-based community provide the highest reduction in uncertainty about that communities activity or inactivity on Twitter. Interestingly, among the highest PV-AC users in these communities---those with highest transfer entropy on average---we find @Colorado, which is the state official Twitter account, @ConnectColorado, a page created to connect Coloradans, and the CBS Denver account, a popular news agency. This means that these accounts have high predictive capacity in terms of their followers' activity on Twitter. This is not surprising as these activity-based communities heavily overlapped with the topic-based communities that discuss Colorado (mentioned above) and these accounts provide information on this topic. This provides a brief proof of concept that this measure makes sense and suggests this could be a useful measure for identifying individuals who possess high predictive capacity for a communities activity on a social media network. However, more work needs to be done to quantify this more fully.

At the individual-based level, we also found some interesting examples of multifaceted community membership, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to.
For example, the user @JohnReaves belongs to two different topic communities: one about healthcare and the other about innovation and creativity. There is a $~70\%$ overlap between the innovation and creativity topic community, the interaction-based, and the activity-based community the user is in, whereas there is almost no overlap between the latter two and the healthcare community. This means that the user interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
Another interesting example is given by user @jenajean. She also belongs to two different topic communities: she talks about NASA and space but she does not interact nor behave alike people belonging to that topic community, whereas she also talks about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado. The activity-based community they belong to highly overlaps with the topic community (therefore they behave alike the people that talk about Colorado), but they all belong to different interaction-based communities, each of which does not overlap with the topic community but for two users maximum.
